Programs Performance Analysis Toolkit \textit{Adaptor}

### 2013-10-10 keynote/Keynote.tex
Finish the initial version

\title{Programs Performance Analysis Toolkit}
\author{Michael Pankov}
\institute{Bauman Moscow State Technical University}
\date{June 19, 2013}

@@

\begin{block}{Tasks}
	\begin{enumerate}
		\item Develop method of programs performance modeling 
		\item Implement the programs performance analysis \& modeling toolkit
		\item Study the efficiency of programs performance modeling toolkit on a set of benchmarks
	\end{enumerate}
\end{block}

\begin{block}{Importance}
	\begin{enumerate}
		\item Estimation of computer performance during its design (see co-design)
		\item Search of optimal compiler settings by methods of iterative compilation and machine learning-driven techniques
	\end{enumerate}
\end{block}

@@

\begin{frame}
\frametitle{Method of statistical programs performance analysis ''Velocitas''}

@@

	\begin{columns}[T]
		\begin{column}{0.5\textwidth}
			\begin{itemize}
				\item Calibrates the program execution time measurement before every series of runs
				\begin{itemize}
					\item Subtracts the execution time of ''simplest'' program to avoid systematical error
					\item Runs the program being studied until relative  dispersion of time measurement becomes pretty low ($d_{rel} < 5\%$)
				\end{itemize}
				\item Passes the experiment data to the database interaction module
			\end{itemize}
		\end{column}
		\begin{column}{0.5\textwidth}
			\begin{figure}
				\includegraphics[width=\textwidth]{console}
			\end{figure}
		\end{column}
	\end{columns}

@@

\begin{frame}
\frametitle{k Nearest Neighbors model of performance of \textit{symm} program on \textit{Q8200} CPU}
\begin{center}
\includegraphics[scale=0.2]{symm-knn-q8200}
\end{center}
\end{frame}

>>>>

\title{Programs Performance Analysis Toolkit \textit{Adaptor}}
\author{Michael K. Pankov\\Advisor: Anatoly P. Karpenko}
\institute{Bauman Moscow State Technical University}
\date{\today}

@@

\begin{block}{Tasks}
	\begin{enumerate}
		\item Develop method of programs performance modeling 
		\item Implement the performance analysis \& modeling toolkit
		\item Study the efficiency of toolkit on a set of benchmarks
	\end{enumerate}
\end{block}

\begin{block}{Importance}
	\begin{enumerate}
		\item Estimation of computer performance during its design
		\item Search of optimal compiler settings by methods of iterative compilation and machine learning-driven techniques
	\end{enumerate}
\end{block}

@@

\begin{frame}
\frametitle{Method of statistical programs performance analysis \textit{Velocitas}}

@@

	\begin{columns}[T]
		\begin{column}{0.5\textwidth}
			\begin{itemize}
				\item Calibrates the program execution time measurement before every series of runs
				\begin{itemize}
					\item Subtracts the execution time of ''simplest'' program to avoid systematical error
					\item Runs the program being studied until relative  dispersion of time measurement becomes pretty low ($d_{rel} < 5\%$)
				\end{itemize}
				\item Passes experiment data to database interaction module
			\end{itemize}
		\end{column}
		\begin{column}{0.5\textwidth}
			\begin{figure}
				\includegraphics[width=\textwidth]{console}
			\end{figure}
		\end{column}
	\end{columns}

@@

\begin{frame}
\frametitle{Resulting model of performance}
	\begin{columns}
		\begin{column}{0.3\textwidth}
			\textit{k Nearest Neighbors} model of~performance of~\textit{symm} program on~\textit{Intel Core~2~Quad Q8200} CPU
		\end{column}
		\begin{column}{0.7\textwidth}
			\includegraphics[scale=0.2]{symm-knn-q8200}
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}
\frametitle{Resulting model of performance}
	\begin{columns}
		\begin{column}{0.5\textwidth}
			Comparison of models of performance of \textit{ludcmp} program
		\end{column}
		\begin{column}{0.5\textwidth}
			\includegraphics[scale=0.5]{ludcmp-learners-2}
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}
\frametitle{Where models fail}
	\begin{columns}
		\begin{column}{0.4\textwidth}
			\begin{itemize}
				\item \textit{Amazon} throttles its micro servers: data is split into two ''curves''
				\item \textit{Earth Regression} at least tries to follow the ''main curve''
				\item \textit{k Nearest Neighbors} is much worse in this situation
			\end{itemize}
		\end{column}
		\begin{column}{0.6\textwidth}
			\includegraphics[scale=0.175]{failure-zeon}
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}
\frametitle{Results of evaluation}
	\begin{itemize}
		\item Most suitable Feature Ranking method --- \textit{Earth Importance}
		\item Most suitable Regression method --- \textit{k Nearest Neighbors}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Further work}

	\begin{itemize}
		\item \textit{Velocitas} method is promising, scales for larger feature sets
		\item Data filtering to reduce noise can help it to get even better
		\item \textit{Orange} is decent statistical framework, but interactive work with it limits batch processing
		\item For larger data sets and increased automation of \textit{Adaptor} framework, either its API, or other libraries (e.g. \textit{sklearn}) should be used
		\item Custom research scenario support is required
		\item It would be interesting to perform experiments on GPU to study effects of massive parallel execution
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Thank you!}

	\begin{itemize}
		\item Contact information: Michael K. Pankov
		\begin{itemize}
			\item michaelpankov.com
		\end{itemize}
		\item This is an extended and edited version of my diploma defense keynote, given on June 19, 2013
	\end{itemize}
\end{frame}
